The evolution of gene expression in the term placenta of viviparous mammals

### 2015-11-21 manuscript/manuscript.Rnw
discuss start of OUCH analysis

We used the software OUCH (Ornstein–Uhlenbeck for Comparative
Hypotheses) in the R statistical environment to investigate
significant shifts in gene expression levels over
time\cite{Butler.2004:phlogeneticcomparativeanalysis}. OUCH institutes
an Ornstein-Uhlenbeck (OU) model of evolution, which allows for
different optima for quantitative trait values along user-specified
branches of a phylogenetic tree. The OU model explicitly accounts for
change in quantitative trait values by introducing two parameters into
the model of stochastic Brownian motion of change in trait value along
a phylogenetic tree through time. These parameters include, $\theta$,
or an optimum trait value, and $\alpha$, or the strength of selection
(interpreted as “pull” toward the optimum). In addition, the OU model
can also integrate evolutionary change by assuming that each
user-specified set of braches has its own separate OU parameters
\cite{Butler.2004:phlogeneticcomparativeanalysis}.

>>>>

We used the software \ac{OUCH} in the R statistical environment to
investigate significant shifts in gene expression levels over
time\cite{Butler.2004:phlogeneticcomparativeanalysis}. \ac{OUCH}
institutes an \ac{OU} model of evolution, which allows for different
optima for quantitative trait values along user-specified branches of
a phylogenetic tree. The \ac{OU} model explicitly accounts for change
in quantitative trait values by introducing two parameters into the
model of stochastic Brownian motion of change in trait value along a
phylogenetic tree through time. These parameters are $\theta$, an
optimum trait value, and $\alpha$, the strength of selection
(interpreted as “pull” toward the optimum). In addition, the \ac{OU}
model can also integrate evolutionary change by assuming that each
user-specified set of braches has its own separate \ac{OU} parameters
\cite{Butler.2004:phlogeneticcomparativeanalysis}.
